\documentclass{article}

\usepackage{cv}

\begin{document}
    \cvname{Thomas C. Fraser}
    \cvinfo{January 1st, 2018}
    \cvinfo{154 Quarry Ave. Renfrew ON, Canada}
    \cvinfo{www.tcfraser.com}
    \cvinfo{tcfraser@tcfraser.com}
    \cvinfo{+1 (226) 868-0557}

    \section{Objective}
    Studying theoretical physics in the areas of quantum information/foundations, and quantum gravity. An emphasis on computational physics and teaching is also desired.
    \section{Education}
    \begin{educationlist}
        \item{2017 -- 2018}
             {M.Sc., Physics}
             {Perimeter Scholars International Program}
             {Perimeter Institute for Theoretical Physics, Waterloo, ON}
        \item{2012 -- 2017}
             {B.Sc., Mathematical Physics, Honours, Cooperative Program, Astrophysics Specialization}
             {Cumulative Average: \textbf{97.37\%}}
             {University of Waterloo, Waterloo, ON}
        \item{2008 -- 2012}
             {High School Diploma}
             {Specialist High Skills Major (SHSM) in Energy}
             {Renfrew Collegiate Institute, Renfrew, ON}
    \end{educationlist}
    \section{Awards \& Scholarships}
    \begin{awardlist}
        \subfield{Awarded by University of Waterloo}
        \item{2017}{Governor General's Silver Academic Medallion}{Highest Graduating Average in Graduating Class}{}
        \item{2016}{Mike Lazaridis Scholarship}{Theoretical Physics Fellowship at the Perimeter Institute}{\$20,000}
        \item{2015}{Xerox Research Centre of Canada Limited Award}{Best Work-term Report ``Acoustic Modelling Using Mel-Frequency Cepstral Coefficients''}{\$100}
        \item{2015}{C. C. Lim Physics Prize}{Top Marks in Undergraduate Thermodynamics}{\$100}
        \item{2013}{Don E. Brodie Scholarship}{Highest Experimental Physics Lab Performance}{\$600}
        \item{2012}{A. Donald Maynes Scholarship}{Outstanding Academic Record}{\$2500}
        \item{2012}{BMO Undergraduate Entrance Scholarship}{Outstanding Academic Average}{\$5000}
        \item{2012 -- 2017}{Dean's Honour List}{Academic Performance}{}
        \item{2012}{President's Distinction Scholarship}{Entrance Average}{\$2000}
        \subfield{Awarded by Renfrew Collegiate Institute}
        \item{2012}{Governor General's Bronze Academic Medallion}{Highest Graduating Average in Graduating Class}{}
        % 2016 : Mike Lazaridis Scholarship - University of Waterloo $10,000
        % 2016 : Mike Lazaridis Fellowship - Theoretical Physics Fellowship at Perimeter Institute $11,000
        % 2015 : Xerox Research Centre of Canada Limited Award - Best Work-term Report ``Acoustic Modelling Using Mel-Frequency Cepstral Coefficients'' $100
        % 2015 : C. C. Lim Physics Prize - Top Marks in Undergraduate Thermodynamics $100
        % 2013 : Don E. Brodie Scholarship - Highest Experimental Physics Lab Performance $600
        % 2012 : A. Donald Maynes Scholarship - Outstanding Academic Record $2500
        % 2012 : BMO Undergraduate Entrance Scholarship - Outstanding Academic Average $5000
        % 2012 -- Present : Dean's Honour List - Academic Performance
        % 2012 : President's Distinction Scholarship - Entrance Average $2000
        % 2012 : Governor General's Medallion - Top Student
    \end{awardlist}
    \clearpage
    \section{Research \& Work Experiences}
    \begin{experiencelist}
        \item{
            May 2016 -- September 2016
        }{
            \href{http://www.perimeterinstitute.ca}{Perimeter Institute For Theoretical Physics. Waterloo, ON}
        }{
            Mike Lazaridis Fellow
        }{
            Research in quantum foundations studying quantum non-locality from the perspective of causal inference. Discovered new causal compatibility inequalities leading to a better understanding of quantum information resources. Computationally simulated six-entangled qubits and associated measurements to find new entanglement resources. Invented new computational techniques for solving the marginal satisfiability problem capable of out-performing existing methods when large computational networks are required.
        }

        \item{
            September 2015 -- January 2016
            }{
                \href{http://www.sysomos.com}{Sysomos. Toronto, ON}
            }{
                Research \& Development Data Scientist
            }{
                Industry application of varied machine learning methods. Designed algorithms to perform automatic speech recognition on digital video extracted from Twitter. Implemented advanced signal processing techniques to perform acoustic modelling. Worked with a massive parallel computing architecture to process billions of data sources. Designed and built native Android \& iOS apps from scratch. Culminated in award winning paper.
            }

        \item{
            September 2014 -- May 2015
            }{
                \href{http://www.lunarchstudios.com}{Lunarch Studios. Waterloo, ON}
            }{
                Video Game Developer
            }{
                Built an highly-compatible graphics engine that supports dynamic assets loaded asynchronously. Acted as project manager to complete large-scale, internal projects. Developed a highly scalable server platform with integration between multiple software languages. Researched and implemented numerous bin-packing algorithms in order to optimize texture loading performance.
            }

        \item{
            January 2014 -- May 2014
            }{
                \href{http://www.humber.ca}{Humber College. Toronto, ON}
            }{
                Mathematics Tutor
            }{
                Tutored thousands of students one-on-one in fields such as statistics, technical math, engineering, biomechanics, and business. Lead an initiative to write and produce high quality educational videos to help students with their studies. Developed a multi-platform, browser-based student sign-in system in order to collect meaningful statistics to improve effectiveness of math centre. Designed and produced graphic art to promote and develop a mathematics community.
            }

        \item{
            June 2011 -- August 2011
            }{
                \href{http://ottawavalleysolar.com/}{OVG Solar, Inc. Renfrew, ON}
            }{
                Solar Panel Technician
            }{
                Industry level experience engineering, assembling and maintaining numerous solar panel arrays. Worked in a team of carpenters, electricians and skilled engineers under flexible hours across all of eastern Ontario.
            }
    \end{experiencelist}
    % January 2014 - May 2014
    % Mathematics Tutor
    % Humber College. Toronto, ON
    % Tutored thousands of students one-on-one in fields such as statistics, technical math, engineering, biomechanics, and business. Lead an initiative to write and produce high quality educational videos to help students with their studies. Developed a multi-platform, browser-based student sign-in system in order to collect meaningful statistics to improve effectiveness of math centre. Designed and produced graphic art to promote and develop a mathematics community.

    % September 2014 - May 2015
    % Video Game Developer
    % Lunarch Studios. Waterloo, ON
    % Built an highly-compatible graphics engine that supports dynamic assets loaded asynchronously. Acted as project manager to complete large-scale, internal projects. Developed a highly scalable server platform with integration between multiple software languages. Researched and implemented numerous bin-packing algorithms in order to optimize application performance.

    % June 2011 - August 2011
    % Solar Panel Technician
    % OVG Solar, Inc. Renfrew, ON
    % Industry level experience engineering, assembling and maintaining numerous solar panel arrays. Worked in a team of carpenters, electricians and skilled engineers under flexible hours across all of eastern Ontario.

    % May 2016 - September 2016
    % Mike Lazaridis Fellow
    % Perimeter Institute For Theoretical Physics. Waterloo, ON
    % Research in quantum foundations studying quantum non-locality from the perspective of causal inference. Discovered new causal compatibility inequalities leading to a better understanding of quantum information resources. Computationally simulated six-entangled qubits and associated measurements to find new entanglement resources. Invented new computational techniques capable of out-performing existing methods when large computational networks are required.

    % September 2015 - January 2016
    % Research & Development Data Scientist
    % Sysomos. Toronto, ON
    % Industry application of varied machine learning methods. Designed algorithms to perform automatic speech recognition on digital video extracted from Twitter. Implemented advanced signal processing techniques to perform acoustic modelling. Worked with a massive parallel computing architecture to process billions of data sources. Designed and built native Android \& iOS apps from scratch. Culminated in award winning paper.

    \vspace{-20pt}
    \section{Academic Works}
        \academicsection{Invited Talks At Conferences}
        {
            \begin{academiclist}
                \item{November 2016}
                {Quantum Networks Conference at International Institute for Physics, Natal, Brazil}
                {\href{https://github.com/tcfraser/tcfraser.github.io/raw/master/documents/quantum_networks_brazil_2016.pdf}{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario}}
            \end{academiclist}
        }
        \academicsection{Preprints}
        {
            \begin{paperlist}
                \item{September 2017}
                {Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario}
                {Thomas Fraser, Elie Wolfe}
                {\href{https://arxiv.org/abs/1709.06242}{arxiv.org/abs/1709.06242}}
            \end{paperlist}
        }
        \clearpage
        \academicsection{Project Papers}
        {
            \begin{paperlist}
                \item{April 2016}
                {\href{https://github.com/tcfraser/tcfraser.github.io/raw/master/documents/stellar_metallicity.pdf}{Variations in Stellar Metallicity}}
                {Thomas Fraser}
                {The metallicity and age of a star are closely related due to the composition of materials left behind by parent star(s). Older stars were formed when less metal was present and are expected to have lower metallicities. Does low metallicity provide an explanation as to why we have yet to observe any population III stars?}
                \item{January 2016}
                {\href{https://github.com/tcfraser/tcfraser.github.io/raw/master/documents/MFCC.pdf}{Acoustic Modelling Using Mel-Frequency Cepstral Coefficients}}
                {Thomas Fraser}
                {A technical report detailing the effectiveness of using Mel-frequency cepstral coefficients for audio classification tasks. Numerous audio features and signal processing techniques are considered for comparison. Personal implementation achieves classification accuracies commensurate to winners of international competitions.}
            \end{paperlist}
        }
        \academicsection{Course Notes (Hyperlinked)}{
            \begin{coursenotelist}
                \item{Winter 2016}{\href{https://github.com/tcfraser/course-notes/raw/master/notes/general-relativity/general-relativity.pdf}{General Relativity}}{}
                % {
                %     tensor formalism, Lorentz transformations, Poincare group, foil theories, differential geometry, Einstein field equations, solutions to field equations, black holes \& singularities, cosmology, gravitational waves and perturbation theory, lie derivatives, killing vectors, curvature
                % }
                \item{Winter 2016}{\href{https://github.com/tcfraser/course-notes/raw/master/notes/stat-mech/stat-mech.pdf}{Statistical Mechanics}}{}
                % {
                %     foundations, statistics, laws of thermodynamics, heat capacities, entropy, ensemble theory, micro canonical/canonical/grand canonical, Helmholtz free energy, equipartition and virial theorems, ideal quantum gases
                % }
                \item{Fall 2016}{\href{https://github.com/tcfraser/course-notes/raw/master/notes/applied-probability/applied-probability.pdf}{Applied Probability}}{}
                \item{Fall 2016}{\href{https://github.com/tcfraser/course-notes/raw/master/notes/quantum-physics-three/quantum-physics-three.pdf}{Quantum Physics 3}}{}
                \item{Fall 2016}{\href{https://github.com/tcfraser/course-notes/raw/master/notes/electricity-magnetism-three/electricity-magnetism-three.pdf}{Electricity \& Magnetism 3}}{}
                \item{Fall 2016}{\href{https://github.com/tcfraser/course-notes/raw/master/notes/cosmology/cosmology.pdf}{Cosmology}}{}
                \item{Winter 2017}{\href{https://github.com/tcfraser/course-notes/raw/master/notes/topics-condensed-matter/topics-condensed-matter.pdf}{Topics in Condensed Matter Physics}}{}
            \end{coursenotelist}
        }

        \academicsection{Acknowledgments}
        {
            \begin{paperlist}
                \item{September 2016}
                {\href{https://arxiv.org/abs/1609.00672}{The Inflation Technique for Causal Inference with Latent Variables}}
                {Elie Wolfe, Robert W. Spekkens, Tobias Fritz}
                {}
                \item{August 2016}
                {Qubit Dynamics in Presence of Thermal Noise}
                {John Rinehart}
                { Available upon request.}
                \item{June 2017}
                {\href{https://uwspace.uwaterloo.ca/handle/10012/11998}{Quantum Indefinite Spacetime}}
                {Ding Jia}
                {}
            \end{paperlist}
        }
    \section{Computational Skills}
    \begin{computerlist}
        \item{Languages}
             {C, C++, Python, Mathematica, Matlab, HTML, CSS, Actionscript, JavaScript, Java, Scheme, Basic, LaTeX}
        \item{Methods}
             {Machine Learning, Linear Programming, Graph Theory, Group Theory, PDE Solvers, Linux/Unix Systems, Distributed Systems, Android \& iOS App development}
        \item{Creative Tools}
             {Adobe Suite, AutoCAD 3D, Vector Graphics, Video editing, 3D Animation/Modeling, Graphic Design}
    \end{computerlist}
    \section{Extracurriculars}
    \begin{extralist}
        \item{2015 -- Present}{Personal Mathematics Blog (\href{http://tcfraser.com/}{tcfraser.com})}
        \item{2014 -- Present}{Software Development (\href{https://github.com/tcfraser}{github.com/tcfraser})}
        \item{2007 -- Present}{Acoustic Guitar Player}
        \item{2016 -- 2017}{Physics Interconnected Mentor}
        \item{2013 -- 2017}{Elected Treasurer/Media Officer/Secretary of The UW Physics Society}
        \item{2013 -- 2017}{Undergraduate Year Rep}
        \item{2016 -- 2017}{Intramural Basketball}
        \item{2013 -- 2015}{Member of The Canadian Association of Physicists}
        \item{2013 -- Present}{Independent Graphic Designer}
        \item{2012}{Reach-for-the-Top Trivia Team}
        \item{2012 -- 2013}{Residence Council Member}
        \item{2009 -- 2011}{Member of Ottawa Lions Track \& Field Club}
        \item{2009 -- 2012}{High School Basketball}
    \end{extralist}
    % Countries Traveled
    % Canada
    % United States of America
    % England
    % Scotland
    % Portugal
    % Germany
    % Netherlands
    % Czech Republic
    % Brazil
    % British Virgin Islands
    % Haiti
    \latestrevisionfooter

\end{document}